# These are the Scripts used to get data, clean it, transform it, run prediction algorithms and make analysis

## reading SAS data
# h192dat.sas7bdat

# We have a few datasets in different formats. (h155.dta, h)

Install required packages. Run this only once
```{r}
#install.packages("rmarkdown")
#install.packages('knitr')
#install.packages("foreign")
#install.packages("dplyr")
#install.packages("eeptools")
#install.packages("utf8")
#install.packages("bindr")
#install.packages("crayon")
#install.packages("pillar")
#install.packages("purrr")  
#install.packages("bindrcpp")
#install.packages("magrittr")
#install.packages("pkgconfig")
#install.packages("R6")
#install.packages("tibble")
#install.packages("tidyselect")
#install.packages("plogr")


library("tibble")
```

Note: Loading Hmisc failed. Might wanna use a different package for this *******************TO DO******************

mydata <- sasxport.get("c:/mydata.xpt") => Not working. Fix/find alternative  *******************TO DO******************

Set the working Directory
```{r}
setwd("C:/GATECH/CS 6460 Ed Tech")
```

load required libraries. Run this every time
```{r}

#library(Hmisc)

library(foreign)
#library("knitr")
#library("dplyr")
#library(eeptools)
```

To import a dataset from Stata into R, the function read.dta() from foreign package is used. More specifically look the code below:
It returns 38,974 observations of 1883 variables
```{r}

df <- read.dta("h155.dta")


```

Now, I wanna reduce the dataset to only columns asscosiated with cancer
Currently values are :1-Yes, has Cancer
                      2-No cancer
                     -1-Inapplicable
Eventual goal is to change  values 2 and 3 to 0 so that: 
                      1 = Yes and 0=No
1st I created a new column "positivediag". This will be used to store a value of 1 or 0 based on positive diagnoisis
```{r}
cancer <-df[1:100,c("duid","pid","dupersid","famid31","cabladdr","cabrain","cabreast","cacervix","cacolon","caleukem","calung","calymph","camelano","cancerdx","caother","caprosta","caskindk","caskinnm","cathroat","cathyrod")]

cancer$postiveDiag<- NA
View(cancer)
```

```{r}

```


Now we need to update the value of positiveDiag based on the preceding columns
junk$nm[junk$nm == "B"] <- "b"

cancer$cathyrod[cancer$cathyrod==2]<-0

```{r}

cancer$cathyrod[cancer$cathyrod!='1' ]<-0
cancer$cathroat[cancer$cathroat!='1']<-0
cancer$caskinnm[cancer$caskinnm!='1' ]<-0
cancer$caskindk[cancer$caskindk!='1']<-0
cancer$caprosta[cancer$caprosta!='1']<-0
cancer$caother[cancer$caother!='1']<-0
cancer$cancerdx[cancer$cancerdx!='1']<-0
cancer$camelano[cancer$camelano!='1']<-0
cancer$calymph[cancer$calymph!='1']<-0
cancer$calung[cancer$calung!='1']<-0
cancer$caleukem[cancer$caleukem!='1']<-0
cancer$cacolon[cancer$cacolon!='1']<-0
cancer$cacervix[cancer$cacervix!='1']<-0
cancer$cabreast[cancer$cabreast!='1']<-0
cancer$cabrain[cancer$cabrain!='1']<-0
cancer$cabladdr[cancer$cabladdr!='1']<-0


cancer$cathyrod[cancer$cathyrod==2 ]<-0
cancer$cathroat[cancer$cathroat==2]<-0
cancer$caskinnm[cancer$caskinnm==2 ]<-0
cancer$caskindk[cancer$caskindk==2]<-0
cancer$caprosta[cancer$caprosta==2]<-0
cancer$caother[cancer$caother==2 ]<-0
cancer$cancerdx[cancer$cancerdx==2]<-0
cancer$camelano[cancer$camelano==2 ]<-0
cancer$calymph[cancer$calymph==2 ]<-0
cancer$calung[cancer$calung==2 ]<-0
cancer$caleukem[cancer$caleukem==2 ]<-0
cancer$cacolon[cancer$cacolon==2 ]<-0
cancer$cacervix[cancer$cacervix==2 ]<-0
cancer$cabreast[cancer$cabreast==2 ]<-0
cancer$cabrain[cancer$cabrain==2 ]<-0
cancer$cabladdr[cancer$cabladdr==2 ]<-0

#Now lets change the -1 values to 0 too
cancer$cathyrod[cancer$cathyrod=='-1']<-0
cancer$cathroat[cancer$cathroat=='-1']<-0
cancer$caskinnm[cancer$caskinnm=='-1']<-0
cancer$caskindk[cancer$caskindk=='-1']<-0
cancer$caprosta[cancer$caprosta=='-1']<-0
cancer$caother[cancer$caother=='-1']<-0
cancer$cancerdx[cancer$cancerdx=='-1']<-0
cancer$camelano[cancer$camelano=='-1']<-0
cancer$calymph[cancer$calymph=='-1']<-0
cancer$calung[cancer$calung=='-1']<-0
cancer$caleukem[cancer$caleukem=='-1']<-0
cancer$cacolon[cancer$cacolon=='-1']<-0
cancer$cacervix[cancer$cacervix=='-1']<-0
cancer$cabreast[cancer$cabreast=='-1']<-0
cancer$cabrain[cancer$cabrain=='-1']<-0
cancer$cabladdr[cancer$cabladdr=='-1']<-0

View(cancer)
```



```{r}
#type(cancer$cabreast)
install.packages("plyr")

library("plyr")

```




```{r}
revalue(cancer$cathyrod)
```


















